Project Notes - Installability

### 2020-05-19 StateOfPractice/Peter-Notes/Peter-Notes-Installability.tex
added bare bones installation check advice to installability notes

\begin{enumerate}
	\item Project needs an installation guide.
	\item The installation steps should be linear.
	\item All installation and testing information should ideally be in one document, or in only a few locations. In the latter case the documents should be clearly mapped.
	\item The development environment should be indicated. Specify operating system and libraries used when developing the system. Specify the exact versions. Also specify programming language versions.
	\item The installation guide should lay out all steps to install the program on a fresh virtual box/operating system. The assumption should be that absolutely nothing has been installed on the box. The guide should specify which operating system version is used to install the system using the installation guide. 
	\item The installation guide should indicate all library versions that are required, including those libraries required to view any visual output.
	\item Test cases should be available.
	\item The document should state the steps required to run a test case. 
	\item Test case solutions should be provided. 
\end{enumerate}

>>>>

\begin{enumerate}
	\item Project needs an installation guide.
	\item The installation steps should be linear.
	\item All installation and testing information should ideally be in one document, or in only a few locations. In the latter case the documents should be clearly mapped.
	\item The development environment should be indicated. Specify operating system and libraries used when developing the system. Specify the exact versions. Also specify programming language versions.
	\item The installation guide should lay out all steps to install the program on a bare bones virtual box/operating system. The assumption should be that absolutely nothing has been installed on the box. The guide should specify which operating system version is used to install the system using the installation guide. 
	\item The installation process should be checked using a bare bones virtual machine
	\item The installation guide should indicate all library versions that are required, including those libraries required to view any visual output.
	\item Test cases should be available.
	\item The document should state the steps required to run a test case. 
	\item Test case solutions should be provided. 
\end{enumerate}
